%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  % \cventry
  %   {Chief Advisor} % Job title
  %   {Delta Solutions Consultancy} % Organisation
  %   {Online} % Location
  %   {July 2023 - Current} % Date(s)
  %   {
  %     \begin{cvitems}
  %       \item {Specialize in EDI data analysis, focusing on data science and AI consultations.}
  %       \item {Lead strategic consultations for diverse clients to promote inclusivity in the tech industry.}
  %     \end{cvitems}
  %   }

  \cventry
    {Principal Investigator} % Job title
    {The Alan Turing Institute} % Organisation
    {England, UK} % Location
    {August 2023 - Current} % Date(s)
    {
      \begin{cvitems}
        \item {Directed collaborations with health sector industry partners.}
        \item {Facilitated research into toxicity prediction in drug discovery}
        \item {Extensive use of Machine Learning and AI to develop novel solutions to industry problems.}
      \end{cvitems}
    }

  \cventry
    {Research Data Scientist} % Job title
    {The Alan Turing Institute} % Organisation
    {England, UK} % Location
    {July 2022 - Current} % Date(s)
    {
      \begin{cvitems}
        \item {Managed projects ranging from climate simulations to AI-guided pandemic policies.}
        \item {Offered consultation to academic collaborators and mentored staff through Turing's development program.}
        \item {Developed reproducible pipelines for climate change projections and contributed to open-source software education.}
        \item {Championed EDI initiatives and fostered partnerships to further diversity goals.}
        \item {\textbf{Technical Skills:} C/C++, Python, Linux, Azure, Scripting, Git.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Mentoring, Collaboration.}
      \end{cvitems}
    }

  \cventry
    {Editor} % Job title
    {Journal of Open Source Software (JOSS)} % Organisation
    {Online} % Location
    {September 2022 - Current} % Date(s)
    {
      \begin{cvitems}
        \item {Volunteer position; reviewed submissions and coordinated publication processes.}
        \item {Enhanced and debugged the JOSS web portal for article submissions.}
        \item {\textbf{Technical Skills:} Git, Code Reviewing.}
        \item {\textbf{Soft Skills:} Leadership, Time Management, Communication.}
      \end{cvitems}
    }

    \cventry
    {Research Software Engineer (X-ray Image Analyst)} % Job title
    {Doonan Lab} % Organisation
    {Wales, UK} % Location
    {2017 - 2018 } % Date(s)
    {
      \begin{cvitems}
        \item {Pioneered novel methods for x-raying wheat to study morphometric traits, employing cutting-edge AI techniques.}
        \item {Developed automated systems for high-throughput x-ray image data extraction, crucial for understanding crop response to climate change variables like drought and temperature conditions.}
        \item {Facilitated research that contributed to significant findings on the domestication and evolution of crops, with results and developed methodologies made open-source.}
        \item {Worked collaboratively to address challenges in semantic segmentation and statistical analysis of large-scale 3-D image datasets.}
        \item {\textbf{Technical Skills:} Data Analysis, AI Solutions, Semantic Segmentation, Statistical Analysis.}
        \item {\textbf{Soft Skills:} Teamwork, Problem-solving, Interdisciplinary Collaboration.}
      \end{cvitems}
    }


  \cventry
    {Research Scientist} % Job title
    {National Plant Phenomics Centre} % Organisation
    {Wales, UK} % Location
    {2016 - 2017 } % Date(s)
    {
      \begin{cvitems}
        \item {Analyzed biological data for research studies.}
      \end{cvitems}
    }

  \cventry
    {Teaching Assistant} % Job title
    {Computer Science Department, Aberystwyth University} % Organisation
    {Wales, UK} % Location
    {2015 - 2018} % Date(s)
    {
      \begin{cvitems}
        \item {Instructed undergraduates in programming practices.}
      \end{cvitems}
    }

  \cventry
    {Systems Developer} % Job title
    {Belfast Metropolitan College} % Organisation
    {Ireland} % Location
    {2013 - 2014} % Date(s)
    {
      \begin{cvitems}
        \item {Led a comprehensive system upgrade across the college.}
      \end{cvitems}
    }

  \cventry
    {Gymnastics Coach} % Job title
    {Salto National Gymnastics Centre} % Organisation
    {Ireland} % Location
    {2012 - 2014 } % Date(s)
    {
      \begin{cvitems}
        \item {Trained elite gymnasts to achieve international recognition.}
      \end{cvitems}
    }

\end{cventries}
