%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------


\cvsection{Charity and Volunteer work}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {The Alan Turing Institute}
    {Alan Turing Podcast} % Interest
    {England, UK}
    {2022 - Current}
    { \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Organising and coordinating schedules.}
        \item {Use of professional recording equipment and software.}
        \item {Research and preparation for interviewing.}
      \end{cvitems}} % Description

  \cventry
    {Various}
    {Equality, Diversity and Inclusivity} % Interest
    {England, UK}
    {2020 - Current}
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performing data analysis on recruitment data at Turing and making reports and summaries.}
        \item {Running workshops and training courses aimed at diversifying STEMM.}
        \item {Creating collaborations with various networks via my work at Turing.}
        \item {Giving talks at events.}
        \item {Appearing on panels at conferences.}
        \item {Participating in diversity focused groups such as PyLadies Slack channels.}
      \end{cvitems} } % Description
    
   \cventry
    {The Brilliant Club}
    {Teacher} % Interest
    {England, UK}
    {2019 - Current}
    {\begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Course development.}
        \item {Lesson planning.}
        \item {Teaching Ages 11-18 in schools.}
        \item {Homework marking, grading and feedback.}
      \end{cvitems}} % Description

   \cventry
    {Various}
    {Scientific Outreach} % Interest
    {UK}
    {2018 - Current}
    {\begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Pint of Science talk.}
        \item {Appearing on Podcasts.}
        \item {Answering science questions on social media.}
        \item {Speaking at British Computer Society events.}
        \item {Main stage talk at FOSDEM on open source development in science.}
      \end{cvitems}} % Description

   \cventry
    {Various}
    {Open Source Projects} % Interest
    {Online}
    {2017 - Current}
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Actively working to improve equality in Wikipedia articles}
        \item {Submitting pull requests and making bug reports in various open projects}
        \item {Answering questions on forums e.g., Stack Overflow.}
      \end{cvitems}} % Description
    


\end{cventries}